Incentivizing Exploration by Heterogeneous Users

### 2018-02-05 appendix.tex
editted the payment proof

We need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
\begin{lemma}
For all $n\geq 1$, we have
\begin{align}
0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
\end{align}
\label{lemma:cal2}
\end{lemma}
\begin{proof}
\begin{align}
&0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
\iff & 0.81 n^{5/3} \geq 0.6n \log(\log_{1.1}(n)+1) \nonumber \\
\iff &  \frac{81}{60} n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
\end{align}

Denote $f(x) = \frac{81}{60}x^{2/3} - \log(\log_{1.1}(x)+1)$. It's easy to compute $f^{'}(x)=0$ has a unique solution $x_{0}=e^{2/3w(\frac{20e^{20000/314763}}{27})-\frac{10000}{104921}}$ (here $w(\cdot)$ is the Lambert W-Function) and it is the global minimum. Since $f(x_{0})\approx 0.0252 >0$, we know $f(x)>0$ for all $x\geq 1$. Thus, our lemma holds true.
\end{proof}

@@

Set $g(n,\ell)$ to be $\frac{2\sigma \ell}{n^{1/6}}$. Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm. Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{2\sigma l}{n^{1/6}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$. Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms. Denote $a_0=\frac{4Wm\sigma}{p^{-1}(\frac{p}{2})}$. In order to have $\frac{2\sigma l}{n^{1/6}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^6 \rceil$. In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_2=\frac{2}{p}$. Thus, we know we can only incur regret for sample paths $\omega$ in the $\ell^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}$ rounds.

Thus,
\begin{align}
\sum_{t=1}^{\infty}c(t)\leq\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\bar{c}(n,\ell)\mathbbm{1}\{\omega\in L[\ell]\}\bar{T}_{n}. \nonumber
\end{align}

@@

\begin{align}
&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\bar{c}(n,\omega)P(\omega \in L(\ell))E[\bar{T}_{n}] \nonumber \\
=&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+2Wm\frac{2\sigma \ell}{n^{1/6}}\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[\ell])E[\bar{T}_{n}]. \nonumber
\end{align}

@@

We now bound $P(\omega\in L[\ell])$ for $n\geq n_0$ and $\ell\geq 2$. As a reminder, we omit the dependency between $\epsilon_{i,t}^{j}$, $n$ and $\omega$. We know 
\begin{align}
&P(\omega\in L[\ell]) \nonumber \\
=&P(\omega\in L^{'}[\ell])- P(\omega\in L^{'}[\ell-1]) \nonumber \\
\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{2\sigma (\ell-1)}{n^{1/6}}, \forall i,j\right) \nonumber \\
=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (\ell-1)}{n^{1/6}}\right) \nonumber  \\
\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (\ell-1)}{n^{1/6}}\right) \nonumber
\end{align}

Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,
\begin{align}
&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(\ell-1)}{n^{1/6}}\right) \nonumber \\ 
=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{N(i,t)(\ell-1)}{n^{1/6}}\right) \nonumber \\
\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(\ell-1)). \nonumber
\end{align}

Based on Lemma~\ref{lemma:cal2}, we know
\begin{align}
&N(i,t)^{5/6}(\ell-1) \nonumber \\
=& 0.9N(i,t)^{5/6} + N(i,t)^{5/6}(\ell-1.9) \nonumber \\
\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(\ell-1.9)^2 N(i,t)} \nonumber \\
\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(\ell-1.9)^2 N(i,t)}. \nonumber
\end{align}

Based on Lemma~\ref{ACI-inequality}, we know
\begin{align}
& P(\omega\in L(\ell) \nonumber \\
\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(\ell-1)) \nonumber \\
\leq & \sum_{i,j}24e^{-1.8(\ell-1.9)^2} = 24Nme^{-1.8(\ell-1.9)^2}. \nonumber
\end{align}

@@

Thus,
\begin{align}
&\sum_{t=1}^{\infty}c(t) \nonumber \\
\leq&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(\omega\in L[1])E[\bar{T}_{n}] +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]E[\bar{T}_{n}] +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}E[\bar{T}_{n}]\nonumber \\
\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]Nn +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}Nn \nonumber \\
\leq & \left[R+4Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^6 \rceil\})^2+\sum_{\ell=2}^{\infty}24N^2 m[R+4Wm\ell\sigma](\max\{n_2,\lceil (a_0 \ell)^6 \rceil\})^2 e^{-1.8(\ell-1.9)^2} \nonumber \\
=& O(N^2). \nonumber
\end{align}

>>>>

We need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
\begin{lemma}
For all $n\geq 1$, we have
\begin{align}
5n^{3/5} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
\end{align}
\label{lemma:cal2}
\end{lemma}
\begin{proof}
\begin{align}
&5 n^{3/5} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
\Longleftarrow &  25 n^{6/5} \geq n \log(\log_{1.1}(n)+1) \nonumber  \\
\Longleftarrow &  25 n^{1/5} \geq \log(\log_{1.1}(n)+1) \nonumber \\
\Longleftarrow &  25 n^{1/5} \geq \log_{1.1}(n)+1. \nonumber 
\end{align}

Denote $f(x) = 25x^{1/5} - \log_{1.1}(x)-1$. Set it's first derivate to $0$, we get its global mimumum at $x_0=\frac{161051}{3125}$ and $f(x_0)> 0$. Thus, our Lemma holds true.

@@

Set $g(n,\ell)$ to be $\frac{12\sigma \ell}{n^{2/5}}$. Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm. Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{12\sigma l}{n^{2/5}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$. Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms. Denote $a_0=\frac{24Wm\sigma}{p^{-1}(\frac{p}{2})}$. In order to have $\frac{12\sigma l}{n^{2/5}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^\frac{5}{2} \rceil$. In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_2=\frac{2}{p}$. Thus, we know we can only incur regret for sample paths $\omega$ in the $\ell^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}$ rounds.

Thus,
\begin{align}
\sum_{t=1}^{\infty}c(t)\leq\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(n,\ell)\mathbbm{1}\{\omega\in L[\ell]\}\bar{T}_{n}. \nonumber
\end{align}

@@

\begin{align}
&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(n,\omega)P(\omega \in L(\ell))E[\bar{T}_{n}] \nonumber \\
=&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[R+2Wm\frac{12\sigma \ell}{n^{2/5}}\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[R+24Wm\sigma l\right]P(\omega\in L[\ell])E[\bar{T}_{n}]. \nonumber
\end{align}

@@

We now bound $P(\omega\in L[\ell])$ for $n\geq n_0$ and $\ell\geq 2$. As a reminder, we omit the dependency between $\epsilon_{i,t}^{j}$, $n$ and $\omega$. We know 
\begin{align}
&P(\omega\in L[\ell]) \nonumber \\
=&P(\omega\in L^{'}[\ell])- P(\omega\in L^{'}[\ell-1]) \nonumber \\
\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{12\sigma (\ell-1)}{n^{2/5}}, \forall i,j\right) \nonumber \\
=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{12\sigma (\ell-1)}{n^{2/5}}\right) \nonumber  \\
\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{12\sigma (\ell-1)}{n^{2/5}}\right) \nonumber
\end{align}

Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,
\begin{align}
&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{12\sigma(\ell-1)}{n^{2/5}}\right) \nonumber \\ 
=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{6N(i,t)(\ell-1)}{n^{2/5}}\right) \nonumber \\
\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq 6N(i,t)^{3/5}(\ell-1)). \nonumber
\end{align}

Based on Lemma~\ref{lemma:cal2}, we know
\begin{align}
&6N(i,t)^{3/5}(\ell-1) \nonumber \\
=& 5N(i,t)^{3/5} + N(i,t)^{3/5}(\ell-1) \nonumber \\
\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(\ell-1)^2 N(i,t)} \nonumber \\
\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(\ell-1)^2 N(i,t)}. \nonumber
\end{align}

Based on Lemma~\ref{ACI-inequality}, we know
\begin{align}
& P(\omega\in L(\ell) \nonumber \\
\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq 6N(i,t)^{3/5}(\ell-1)) \nonumber \\
\leq & \sum_{i,j}24e^{-1.8(\ell-1)^2} = 24Nme^{-1.8(\ell-1)^2}. \nonumber
\end{align}

@@

Thus,
\begin{align}
&\sum_{t=1}^{\infty}c(t) \nonumber \\
\leq&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[R+24Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24Wm\sigma \right]P(\omega\in L[1])E[\bar{T}_{n}] +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[R+24Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24Wm\sigma \right]E[\bar{T}_{n}] +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[R+24Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}E[\bar{T}_{n}]\nonumber \\
\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24Wm\sigma \right]Nn +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[R+24Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}Nn \nonumber \\
\leq & \left[R+24Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^{5/2} \rceil\})^2+\sum_{\ell=2}^{\infty}24N^2 m[R+24Wm\ell\sigma](\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\})^2 e^{-1.8(\ell-1.9)^2} \nonumber \\
=& O(\frac{N}{p^5}+ \frac{N^2}{p^5}). \nonumber
\end{align}
